Transforming Trash as an Artistic Act

### 2015-12-06 chapter3_reduced.tex
Reduction
Former-commit-id: 776addea2a8d261fe4b62f86718a2555ef817347

\epigraph{One day, in a rubbish heap, I found an old bicycle seat lying beside a rusted handlebar, and my mind instantly linked them together. I assembled these two objects, which everyone then recognized as a bull’s head. The metamorphosis was accomplished, and I wish another metamorphosis would occur in the reverse sense. If my bull’s head were thrown in a junk heap, perhaps one day some boy would say, \quotes{Here’s something that would make a good handlebar for my bicycle!}}{\hfill ---Pablo Picasso, \textit{Trashformations}}

Its roots go all the way back to the 1800s in Europe.

How and why does trash draw attention of artists(, and also mine)? In this chapter how artist approached to the trash and their techniques are discussed in the context of art. (Historical development, methodologies, tactics, motivations\ldots) Focused on visual (plastic) arts(, because there is also a music genre called as trash music?). How does it turn to medium?

% TODO List motivations of artists and their ideas about junk. Because it reveals the different dimensions of this topic.

% Diğer tezlerde ne diyordu. Bu nasıl bir anlatış biçimi be mustafa. doğru düzgün bir şey yok. Anlatcak olsan birisine böyle mi anlatırsın ha?

%%%
%%%
%%%
\section{Root in the Art History}
In this chapter root of using ---(non-art)--- objects in the artworks is examined. In other words using objects in artworks beyond their intended purpose or intended meaning and function. Developing artworks not only painting but also using paper and other stuff by pasting them together. (Foundations of trash in art.) Using object apart from their proposed meaning is not a new thing[ref required, using jewelry by African tribes], through the ages people used objects and tools for different purposes. However it is not discussed in the context of (western)art and not accepted method for art making. Therefore who and which work introduces this concept and how it is developed and evolved in time. (of course it is a brief overview by some remarkable pieces.)

@@

\todo[inline]{örnek bulduğum tezlerin izlediği yolu burda izleyebilirim.}

%****************************************
% FROM The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
% The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed.
% Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality.
% Karl Marx had already written that economic value does not inhere in the materiality of the object but emerges from the social relations and organisation of labour which produces it, and that the separation between consumer market and the sphere of culture had become indiscernible.
% Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay. \ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed. As he wrote: ‘It grows more or less according to the principle of a metropolis.’ 13 The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality. Material has transformed into information, and ‘how’ has surpassed ‘what’ we see. The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin. As Schwitters wrote: ‘One can even shout out through refuse.’ 14 His words still echo.
%........................................

%%
%%
\subsection{Collage}
Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or “found” materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting. In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions. Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}.

% Works of picasso baraque.

% TODO reading...
\cite{greenberg1984collage}

%%
%%
\subsection{Assemblage}
Assemblage work produced by the incorporation of everyday objects into a composition. It is similar to collage, but main difference is that assemblage is three dimensional rather collage is two-dimensional. Diverse range of things can be used production of work. In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art. William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}.

\todo{Joseph Cornell, assemblage artist.}

%%
%%
\subsection{Bricolage}
Dictionary meaning; something constructed using whatever was available at the time.

% daha öncesinde birbiri ile bağlantılı olmayan nesne, söylem, metin, form, pratik vs. gibi şeyleri yeni bağlamlarda yeni anlamlar üretmek için montajlama, yap-boz edimi;

% ingilizcesi do-it-yourself anlamına gelen fransızca bir kelime. bunu yapan kişiye de bricoleur deniyormuş. lévi-strauss'un kitapları ingilizce'ye çevrilirken diy/craftsman tam olarak anlamı karşılayamadığından çevirilerde de bricolage olarak kalması tercih edilmiş. kendi başına da anlamlı olan öğelerin yeni bir bağlam çerçevesinde birleştirilmesi ve bu parçalardan yeni hikayeler, efsaneler yaratılması edimine de entelektüel brikolaj diyebiliyormuşuz.

Claude Levi-Strauss notes: the bricoleur works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available. It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old. \cite{levi1966savage}

the “bricoleur” is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}

@@

\ldots someone that creates bricolage is described as a \quotes{bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends}.

@@

% TODO reading...
[TODO use this ref]\cite{strasser1999waste}

Bricolage is different than collage. Bricolage > collage. Because it is more general understanding of human practice. Collage is just only gluing paper together and it can be only a subset of bricolage. Same applicable for assemblage. Transforming trash can be examined within bricolage.

%%
%%
\subsection{Found Object (Ready-mades)}
Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function. Pablo Picasso first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912). Marcel Duchamp is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art. The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.

% Duchamp falan.

\todo[inline]{place in the folk art.}

%%
%% junkyard art
\subsection{Garbage Art, Recycling Art}
"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts. This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}

%%%
%%%
%%%
\section{The case of \quotes{The Gleaners and I}}
The Gleaners and I is a 2000 French documentary film by Agnès Varda that features various kinds of gleaning. The Gleaners and I is notable for its fragmented and free-form nature along with it being the first time Varda used digital cameras. This style of film making is often interpreted as a statement that great things like art can still be created through scraps, yet modern economies encourage people to only use the finest product.

@@

%%%
%%%
%%%
\section{Examples from contemporary artists}
Artist and artworks related with trash and their analysis. Stages of their works and methods. (Keep in mind that what can be extracted from these works?) There are a lot of work that needs to mentioned here but to stay focused and not to move away from the scope of the thesis only the works are selected with relation to the theory chapter. (is it really like that?)

% FROM ReVista
Trash is dirty. Trash is smelly. Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.

% FROM Paola Ibarra ReVista
Whether in sculpture, photography or other media, art frequently deals, directly or by allusion, with daily challenges of life in Latin America and elsewhere. Is there a limit to recycling and representation? Or is there a point at which waste cannot become art (or anything else)?

% TODO Naive debate??
All that can be seen as naive act because of little impact and outside of the system(which system?). As it compared to the huge portion of the material the transformed material is so little therefore it can be questioned that it has no impact and worthless as it compared to the mountains of landfill. However this very argumentative that having no impact or little impact. It might be true that this practices solve all problems of landfill or etc. But changes individuals and communities life. It recreate and rebuilds the community. Even if it is one simple object worth look and see the opportunities of it.

\begin{itemize}
% FROM Maite Zubiaurre, Re Vista Garbage
\item \textbf{Road Kill.} Filomena Cruz creates photographic series “Road Kill” painstakingly captures tiny “trash corpses” on the pavement. It is that particular type of trash meet in the public places. trash left behind, trash on the sidewalk, squished, squashed, and weathered. Filomena Cruz sees trash that we don’t want to see. A piece of chewing gum with an “engraved” leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of “worthlessness” suddenly becoming meaningful (and moving).For one thing, trash corpses faithfully record city life.

% They are continuously changing. Unrecognized things. Created unintentionally. Part of the streets roads. It can be seen as a archive.

  \begin{figure}[ht]
      \centering
      \includegraphics[width=0.8\textwidth]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
      \caption{Road Kill by Filomena Cruz}
      \label{fig:FilomenaCruz_RoadKill_ReVista}
  \end{figure}

%\item Pictures of Garbage by Vic Muniz
\item \textbf{Pictures of Garbage.} Vic Muniz creates monumental trash art in Jardim Gramacho with the help of \textit{catadores} (Waste Land, 2010) Waste Land, directed by Lucy Walker  tracks the development of a series of monumental photographic portraits made from trash. Called “Pictures of Garbage,” they were created by Mr. Muniz in collaboration with the garbage pickers of Jardim Gramacho, an open-air dump just outside Rio that is one of the largest landfills in Latin America. (Important point is here collaboration with the pickers. Listening their stories and capturing their portraits. What is specific about trash here?)

% Talking with people picks up trash. Goes to landfill?

  \begin{figure}[ht]
      \centering
      \includegraphics[width=0.5\textwidth]{graphics/vik-muniz-picturesofgarbage0.jpg}
      \caption{Pictures of Garbage by Vic Muniz}
      \label{fig:VicMuniz_PicturesOfGarbage}
  \end{figure}

\item \textbf{The Recycled Orchestra.} Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their “Recycled Orchestra”. ``The world send us garbage. We send back music''.

"People realize that we shouldn't throw away trash carelessly," says Chavez at the end of the trailer. "Well, we shouldn't throw away people either."

This project can be seen as a bricolage practice. They build their musical instruments from what is available around.

Resistance'a bir örnek. Çünkü müzik yapmak para isteyen bir şey mi? ya da bir senfoni orkestrası kurmak?

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
        \caption{Sax}
        \label{fig:landfill_harmonic-sax}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
        \caption{Violin}
        \label{fig:landfill_harmonic-violin}
    \end{subfigure}
    \caption{Instruments of Recycled Orchestra}\label{fig:animals}
\end{figure}

% Peki bu iş neden sanat işi olsun ki?

% Bambaşka şeylere dönüşen ürünler. Üretim amaçlarının dışında. Yeni linkler bağlantılar kuran müzik aletleri. Kendilerinden beklenmeyeni başarmak vs. Daha önce görülmeyen şeyler, görülmeyen ilişkiler.

% Bunu bir okuyabilirsin.
% http://www.publicbooks.org/interviews/recycling-literary-culture-a-conversation-with-lucia-rosa
% http://www.eloisacartonera.com.ar/ENGversion.html
\item “Eloísa Cartonera,” a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers: \quotes{We purchase [\ldots] cardboard from the
urban pickers (\textit{cartoneros}) who pick it from the streets. Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]

It reminds me that litreary is also a reuse concept. Because to create meanings we reuse words and idioms again again with different combination. \comment{tüm kelimeler vs hepsi sıralanıyor. Arka arkaya getiriliyor. Kelimeler harflerin hepsi tekrar tekrar kullanılıyor. Reused cartbord reminds all of these and as an object all of it...}

\todo[inline]{Bu ne anlama geliyor onu bulmak gerekli. nereye bağlamalı bilemiyorum. Bu ileri dağıtmak gerekiyor ama gene de burada kalanlar var. Ne yapsam ki?}

% FROM Paola Ibarra, ReVista
%\item Forever; Blue Yonder by artist Kyle Huffman
%\item Too Too---Much Much by Thomas Hirschhorn
%\item Autoconstrucción by Abraham Cruzvillegas

% Bu adamın ilkeleri var. Benim de var aslında.
% FROM A Present from the Sea BY SONIA CABANILLAS, ReVista
% https://www.youtube.com/watch?v=v6IoEF_Tsrw
%\item Nick Quijano has some rules to create assemblages. \quotes{There are certain self-imposed rules to this creative process: first, the assemblages or artefactos must all come from material washed ashore on this beach; second, it must be plastic and industrial refuse, result of the processing of fossil fuel; third, it must be polished by a long stay in deep waters, sometimes even encrusted with corals, shells or pebbles, or simply scraped by the ocean floor. As a sign of respect and sacralization, these pieces will be incorporated without any adjustment: no cutting or bending, seen as a mutilation of the object. Its identity cannot be veiled or masked but always must be recognizable amidst the other components; e.g, a comb must remain a comb even as one may see it as a mustache.} The sea returns this refuse; it is not biodegradable.

% FROM Burning Messages BY MICHAEL WELLEN, ReVista
%\item Antonio Berni

>>>>

\epigraph{One day, in a rubbish heap, I found an old bicycle seat lying beside a rusted handlebar, and my mind instantly linked them together. I assembled these two objects, which everyone then recognized as a bull’s head. The metamorphosis was accomplished, and I wish another metamorphosis would occur in the reverse sense. If my bull’s head were thrown in a junk heap, perhaps one day some boy would say, \quotes{Here’s something that would make a good handlebar for my bicycle!}}{\hfill ---Pablo Picasso, \textit{Trashformations}, 1998}

How and why does trash draw attention of artists? In this chapter how artist approached to the trash and their techniques are discussed in the context of art. (Historical development, methodologies, tactics, motivations\ldots) Focused on visual (plastic) arts(, because there is also a music genre called as trash music?). How does it turn to medium?

%
%
\section{Root in the Art History}
Using trashed objects in making of art can be examined with the enterance of non-art objects to art \todo{sadece bu yeterli olmayabilir.}. In other words using objects in artworks beyond their intended purpose or intended meaning and function. Developing artworks not only painting but also using paper and other stuff by pasting (or putting) them together. (How using non-art objects affected art?) \comment{Using object apart from their proposed meaning is not a new thing, through the ages people used objects and tools for different purposes. However it is not discussed in the context of fine art and not accepted method for art making.} First one is a collage work of Picasso. \todo{Still Life with Chair Caning} \todo{Violin with sheet of music}. One of the earliest examples is Picasso’s \quotes{Still Life with Chair Caning} (1912), in which a piece of oilcloth with an imitation chair caning design was pasted onto the painting. This work of Picasso also can be considered as first example of assamblage because of a rope was used to frame the picture. Using non-art objects in the production of art challanges existing conventions of painting. 
% FROM http://www.sparknotes.com/biography/picasso/section7.rhtml
\paraphrase{This was a new way of making art; instead of painting a thing, you could stick whatever it was right onto the canvas. The three letters above the scrap of cloth, "JOU," can be understood as both the beginning of the word "JOURNAL," alluding to the customary newspaper lying across the café table, and as the French verb meaning "to play." The new technique of collage allowed new possibilities of playfulness.} \comment{\textbf{Pablo Picasso} first publicly utilized the idea when he pasted a printed image of chair caning onto his painting titled Still Life with Chair Caning (1912).} \textbf{Marcel Duchamp} is thought to have perfected the concept several years later when he made a series of ready-mades, consisting of completely unaltered everyday objects selected by Duchamp and designated as art. The most famous example is Fountain (1917), a standard urinal purchased from a hardware store and displayed on a pedestal, resting on its side.

% FROM The Ruin and the Ruined in the Work of Kurt Schwitters by Gemma Carroll
\todo{works of Kurt Schwitters} \paraphrase{The German avant-garde was working from ruins literally and metaphorically, and trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed. Schwitters is able to use the ruined, the waste products, as an anthropological exploration of society from both its unpleasant outcomes and its decay. \ldots trash was both practically and freely available; to use it was an action that took the ruins of our society, its discarded, to question how meaning is constructed. As he wrote: ‘It grows more or less according to the principle of a metropolis.’ 13 The Merzbau was itself a city; and just as Marx wrote that it was not the materiality of the object but the social relations that create value, the use of urban detritus in particular, the squalid results of mass-produced human relations, infuses the materiality of Schwitters’ work with an anthropological quality. Material has transformed into information, and ‘how’ has surpassed ‘what’ we see. The grottos in the Merzbau that still reveal this detritus most clearly could not be re-created in Bissegger’s reconstruction because, arguably, they are an exploration of absence, an exploration of ruin.}

@@

%
%
[Collage] Collage originates from the French \textit{coller} is an artistic technique of applying manufactured, printed, or found materials, such as bits of newspaper, fabric, wallpaper, etc., to a panel or canvas, frequently in combination with painting. In about 1912–13 Pablo Picasso and Georges Braque extended this technique, combining fragments of paper, wood, linoleum, and newspapers with oil paint on canvas to form compositions. Pasting paper is not a new technique but using this it in the art making is a revolutionary movement in the  language of art \cite{waldman1992collage}. \todo{read greenberg1984collage}

%
%
[Assemblage] Assemblage work produced by the incorporation of everyday objects into a composition. It is similar to collage, but main difference is that assemblage is three dimensional rather collage is two-dimensional. Diverse range of things can be used production of work. In 1961, the exhibition "The Art of Assemblage" was featured at the New York Museum of Modern Art. William C Seitz, the curator of the exhibition, described assemblages as being made up of preformed natural or manufactured materials, objects, or fragments not intended as art materials \cite{seitz1961art}. \todo{Joseph Cornell, assemblage artist.}

%
%
[Bricolage] Dictionary meaning\todo{which dictionary}; something constructed using whatever was available at the time. \paraphrase{Claude Levi-Strauss notes that the \textit{bricoleur} works not from the principle of making things only if natural resources are available but makes things according to those things at hand, making do with what is available. It is an expression that, like the natural cycles of the Earth, attempts to make something new from something old. \cite{levi1966savage}} The \textit{bricoleur} is \ldots someone who works with his [or her] hands and uses devious means compared to those of a craftsman \ldots \cite{levi1966savage}

\paraphrase{\ldots someone that creates bricolage is described as a \quotes{bricoleur, an odd-job man who works with his hands, employing the bricoles, the scraps or odds and ends}.}

@@

@@

[TODO use this ref]\cite{strasser1999waste}

%
%
[Found Object] Found object originates from the French \textit{objet trouvé}, describing art created from undisguised, but often modified, objects or products that are not normally considered art, often because they already have a non-art function.

%
%
[Ready-Mades]

%
%
\section{Examples from contemporary artists}
Beyond historical development of art with non-art objects and trash, for contemporary artist what it means has slight differences. Firstly their purpose do not want to express the language of art by using trash and non-art objects because they are already done and the way of making art dramatically changed. Therefore what are their purpose and how they can be viewed?

% FROM ReVista
\todo{başka bir yerde kullan. Trash is dirty. Trash is smelly.} \paraphrase{Trash can provide the raw materials for exquisite art---from sculpture to film and beyond.}

% FROM Paola Ibarra ReVista
\paraphrase{Whether in sculpture, photography or other media, art frequently deals, directly or by allusion, with daily challenges of life in Latin America and elsewhere. Is there a limit to recycling and representation? Or is there a point at which waste cannot become art (or anything else)?}

% TODO Naive debate??
\comment{All that can be seen as naive act because of little impact and outside of the system(which system?). As it compared to the huge portion of the material the transformed material is so little therefore it can be questioned that it has no impact and worthless as it compared to the mountains of landfill. However this very argumentative that having no impact or little impact. It might be true that this practices solve all problems of landfill or etc. But changes individuals and communities life. It recreate and rebuilds the community. Even if it is one simple object worth look and see the opportunities of it.}

%
% Tags: "dikkate alınmayanı tekrar ele alıyor". Mekan: sokaklar, şehir, kamusal alan. Traces of our life.
\textbf{Road Kill.} \paraphrase{Filomena Cruz creates photographic series named as \quotes{Road Kill} painstakingly captures tiny \quotes{trash corpses} on the pavement. It is that particular type of trash meet in the public places. Trash left behind, trash on the sidewalk, squished, squashed, and weathered. Filomena Cruz sees trash that people don’t want to see. A piece of chewing gum with an \quotes{engraved} leaf; a flattened-out tube; a corroding paper napkin with a still intact heart; or a frog-green Crayola melting in the heat, all speak the language of \quotes{worthlessness} suddenly becoming meaningful (and moving). For one thing, trash corpses faithfully record city life.} Uses public spaces and takes photos of streets and roads in unfamiliar fashion, focussing onto trash. Captures the trace of city life from trash. She does not collect the trash physically, collects the images of them. They are still there and continously changing.

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/FilomenaCruz_RoadKill_ReVista.jpg}
  \caption{Road Kill by Filomena Cruz}
  \label{fig:FilomenaCruz_RoadKill_ReVista}
\end{figure}

%
%
\textbf{Sad Chair.} can be add here. Very similar to road kill, captures the record of city life. Leaved alone chairs somewhere in the city.

%
%
\textbf{Pictures of Garbage.} Vic Muniz creates monumental portraits from trash in Jardim Gramacho, an open-air dump just outside Rio, with the help of \textit{catadores} in the documentary film (Waste Land, 2010) Waste Land, directed by Lucy Walker. Called “Pictures of Garbage,” they were created by Mr. Muniz in collaboration with the garbage pickers of Jardim Gramacho, an open-air dump just outside Rio that is one of the largest landfills in Latin America. (Important point is here collaboration with the pickers. Listening their stories and capturing their portraits. It methods similar to the mosaics, every type of discard collected from dump used his photos.) Trash and people who live there is the subject of his portraits. None of the trash is belong to that people. However again these trash express them perfectly because they make a life from trash. Their home is dump.

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/vik-muniz-picturesofgarbage0.jpg}
  \caption{Pictures of Garbage by Vic Muniz}
  \label{fig:VicMuniz_PicturesOfGarbage}
\end{figure}

%
%
\textbf{The Recycled Orchestra.} Favio Chávez and Nicolás Gómez decide to build musical instruments out of garbage and get 35 children from Cateura, Paraguay’s biggest trash dump, to travel the world with their \quotes{Recycled Orchestra}.

"People realize that we shouldn't throw away trash carelessly," says Chavez at the end of the trailer. "Well, we shouldn't throw away people either." \quotes{The world send us garbage. We send back music}.

[Critics] This project can be seen as a bricolage practice. They build their musical instruments from what is available around. What they create is actually not expected thing from trash. This work also can be seen as an example of resistence because playing western classical music with their instruments is very costly. To enjoy and play such a music requires economical wealth and it is not possible for everyone. They create their opportunites or turn trash to oppornutiy for them. Here economical restirictions result in great production boost with creativity. After seeing this instruments and listen their music changes peoples mind to the perception of the classical music and the intruments. The original items are well designed and perfect. They have identical outlook(or view). Not only trash is here transformed, but also perception to the trash and instruments are transformed here. After that point trash that you know is no longer same trash. At the same time with music lives of children are changed. They work on unimaginable thing for them. Quality of their music is different than the original one.

\todo{indiginazation of western goods here.}

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-sax.jpg}
        \caption{Sax}
        \label{fig:landfill_harmonic-sax}
    \end{subfigure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{graphics/landfill_harmonic-violin.jpg}
        \caption{Violin}
        \label{fig:landfill_harmonic-violin}
    \end{subfigure}
    \caption{Instruments of Recycled Orchestra}\label{fig:animals}
\end{figure}

% TODO: http://www.publicbooks.org/interviews/recycling-literary-culture-a-conversation-with-lucia-rosa
% http://www.eloisacartonera.com.ar/ENGversion.html
\textbf{Eloísa Cartonera.} a work cooperative in Buenos Aires, proudly produces handmade books with cardboard covers. \quotes{We purchase [\ldots] cardboard from the urban pickers (cartoneros) who pick it from the streets. Our books are on Latin American literature, the most beautiful we had a chance to read in our lives.} \quotes{Some of them are preserved as art books at university libraries, while others circulate as literary pieces expected to disintegrate in time---something anticipated of the material they are made from.} [from PAOLA IBARRA, ReVista]

It reminds me that litreary is also a combination of reused thing. Because to create meanings we reuse words and idioms again and again with different combination.

%
%
\textbf{American Beauty.} The film American Beauty, which features a long, poetic clip of a plastic bag swirling on an eddy of air. It is hard to think of plastic bags as things of beauty. \todo{Bunun hakkında daha fazla bilgiye ihtiyaç var.}

%
% From http://www.thisiscolossal.com/2014/06/historical-fine-oil-portraits-on-crumpled-trash-by-kim-alsbrooks/, http://www.thisiscolossal.com/2015/05/new-historical-portraits-on-flattened-cans-by-kim-alsbrooks/, http://kimalsbrookswhitetrash.blogspot.com.tr/
\textbf{Paintings on beer can.} Kim Alsbrooks, historical oil portraits on flattened beers cans and fast food containers. \quotes{The White Trash Series was developed while living in the South out of frustration with some of the prevailing ideologies, in particular, class distinction. This ideology seems to be based on a combination of myth, biased history and a bizarre sentimentality about old wars and social structures. With the juxtaposition of the portraits from museums, once painted on ivory, now on flattened trash like beer cans and fast food containers, the artist sets out to even the playing field, challenging the perception of the social elite in today’s society.} \quotes{On technique: The trash is found flat, on the street. One cannot flatten the trash. It just doesn't work. It must be found so that there are no wrinkles in the middle and the graphic should be well centered. Then the portraits are found that are complimentary to the particular trash. Generally I depict miniature portraits from the watercolor on ivory era (17th-18th century more or less). The trash is gessoed in the oval shape, image drawn in graphite, painted in oils and varnished.} I need to mention that this images are very subversing to the perception of us about these images. It is unexpected way of presenting images. There is a relationship with the image and painting. At least this work questioned this relation. With tihs work one can ask that with the painting trashed can become valueable thing or with this can this paintiing became valueless. Artsist combines two thing that can be never thought together. New combination, new meaning.

\begin{figure}[ht]
  \centering
  \includegraphics[height=6cm]{graphics/Alsbrooks.jpg}
  \caption{The White Trash Series by Kim Alsbrooks}
  \label{fig:Alsbrooks}
\end{figure}

%
% ARTWORK http://timgaudreau.com/2012/trash/trash.html
[Self-Portrait as Revealed by Trash] Even if most of people pay little attention to the trash, everybody do not. An artist takes photos of his every trash, like a popular habit that is taking photos of face everyday. He focuses on the thing that paid little attention. At the end he exhibits all the photos by covering all the walls of room. It can seen as record of his activities, record of commodities. Most of them we are not aware of them. Draw the attention of is being thrown away and every time and everywhere. They are too much and can only fit covering all the walls. \todo[inline]{Tim Gaudreau Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006} \paraphrase{After photographing my trash over the course of the year, I ended up with 5,000 images representing my waste stream. These collections of grids represent my first experiments with using those images. This initial work ultimately led to the full scale collages that have become my Self-portrait as Revealed by Trash: 365 days of photographing everything I threw out.}

\textbf{Martin Kaltwasser \& Folke Föbberling: City As a Resource.} One Man's Trash Is Another Man's Treasure. Garbage dump or gold mine? The German artistic collaborators Martin Kaltwasser and Folke Köbberling see rubbish as a major resource. Their projects colonize public space in the name of recycling and design: Overnight, they can make pavilions, villages of huts and even whole houses appear. In installations, exhibitions and, most frequently, guerrilla architectural interventions, they question the conditions of urban life as determined by privatization. For example, in a 2004 project called "Hausbau," they built a house in front of West Berlin's infamous Gropius-designed, failed-utopia high-rise development, Gropiustadt, and moved their family into it for a one week stay; for 2005's "Kleinod," they built a bridge and a stairway between a local family's home and a nearby community garden. In City as a Resource: One Man's Trash Is Another Man's Treasure, Köbberling and Kaltwasser propose simple ways of livening up and re-appropriating the urban habitat with sly alternatives to conventional urban planning.

%
% http://www.tate.org.uk/art/artworks/nelson-the-coral-reef-t12859/text-summary
% \textbf{The Coral Reef} Nelson’s breakthrough work was The Coral Reef, which he mounted in 2000 at Matt’s Gallery from objects and debris gathered from alleys, trash bins, and car-trunk sales all over London. The title refers to Nelson’s aim of creating an intricate, reeflike network of lives “all existing under one sea, which is capitalism,” he says. (It is very corralate between Ages Varda's work. She shows at the side of human practice, Nelson looks the topic from object side.)

% FROM Paola Ibarra, ReVista
% Forever; Blue Yonder by artist Kyle Huffman
% Too Too---Much Much by Thomas Hirschhorn
% Autoconstrucción by Abraham Cruzvillegas

% FROM Burning Messages BY MICHAEL WELLEN, ReVista
% Antonio Berni

% Bu adamın ilkeleri var. Benim de var aslında.
% FROM A Present from the Sea BY SONIA CABANILLAS, ReVista
% https://www.youtube.com/watch?v=v6IoEF_Tsrw
% Nick Quijano has some rules to create assemblages. \quotes{There are certain self-imposed rules to this creative process: first, the assemblages or artefactos must all come from material washed ashore on this beach; second, it must be plastic and industrial refuse, result of the processing of fossil fuel; third, it must be polished by a long stay in deep waters, sometimes even encrusted with corals, shells or pebbles, or simply scraped by the ocean floor. As a sign of respect and sacralization, these pieces will be incorporated without any adjustment: no cutting or bending, seen as a mutilation of the object. Its identity cannot be veiled or masked but always must be recognizable amidst the other components; e.g, a comb must remain a comb even as one may see it as a mustache.} The sea returns this refuse; it is not biodegradable.

% FROM Haiti in the Time of Trash BY LINDA KHACHADURIAN, ReVista
% Haiti. When I ask him why he chooses to work in the medium of trash, he replies, \quotes{It gives respect to my city to use the garbage. It shows that everything can be used, and nothing was lost.} (TODO motivation: \quotes{I get more inspiration working with recycled materials because those pieces are unique and can’t be duplicated}) Eugène says that he’s partial to metal, which has become more and more difficult to find because of the clean-up initiative by the city. When I ask him if part of him wishes there were no such effort underway, he answers: \quotes{No. When you have clean streets you have good health, and that is the most important thing.} (This is very strange. It shows that working with trash and being clean healthy is not a contradiction. Both of them exist together.) \quotes{Other people come to Haiti and see junkyards, but we see magical playgrounds,} Jean explains as he watches them.

% \textbf{Aaron Kramer.} His motto: "Trash is the failure of imagination." \cite{meyer2007turning} In addition to concern for the environment, Kramer was drawn to recycled art because of one simple factor---the price. "Free is certainly great, and that was a driving force for me early on in my career," he said.

% \textbf{SOUP} Mandy Barker is an international award winning photographer whose work involving marine plastic debris has received global recognition. The motivation for her work is to raise awareness about plastic pollution in the world's oceans whilst highlighting the harmful affect on marine life and ultimately ourselves.

% http://www.keaggy.com/chairs/sad/12/
% \textbf{Sad chair.} Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.}

% \textbf{ArtBin} Chris Jordan [Trashing Things]
%****************************************
% EVERYTHING CAN BE TRASH. Act of trashing not act of transforming. Trash is like kara delik gibi ışığın odan kaçamaması gibi hiç bir şeyin ondan kaçılmayacağını hissediyor aslında. 
% Michael Landy's Art Bin uses a art gallery to create his dust bin. Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed. Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints. "There's no hierarchy once they are in the bin" All of them are accepted as same. Ultimate equality. Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts. Nothing's too good for the art bin. Everything can fit into the art bin. Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art. As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”. It is a very big glass bin and isolates people. There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin". There is no limitation of throwing away even if art.

% \textbf{Squeezing}

%http://www.smithsonianmag.com/arts-culture/photographer-creates-fine-art-out-trash-we-throw-environment-180951615/?no-ist
% \textbf{Found in Nature} Barry Rosenthal

% \textbf{Compression} César Baldaccini [Trashing Things]

% \textbf{Found Photos}

%
%
\section{The case of \quotes{The Gleaners and I}}
The Gleaners and I is a 2000 French documentary film by Agnès Varda that features various kinds of gleaning. The Gleaners and I is notable for its fragmented and free-form nature along with it being the first time Varda used digital cameras. This style of film making is often interpreted as a statement that great things like art can still be created through scraps, yet modern economies encourage people to only use the finest product.

@@

%%%
%%%
%%%
\section{Summary}
% Turning art making process to a life practice\ldots

% TODO MOVE another chapter.
% Garbage is often viewed as a form of society’s excess---as the unwanted things that are thrown out without regard.
